Drivers of spatial synchrony in giant kelp populations

### 2021-05-14 paper/SupMat.Rnw
last sentence paranthesize ref

\noindent And since $(\beta_1, \beta_2)$ is distributed in the same way as our right-tail associated noise, this proves all metrics based on the distribution of $r_1$ \ref{r1distribution} are the same for left- and right-tail associated noise.

>>>>

\noindent And since $(\beta_1, \beta_2)$ is distributed in the same way as our right-tail associated noise, this proves all metrics based on the distribution of $r_1$ (\ref{r1distribution}) are the same for left- and right-tail associated noise.
